Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-13 tuningpredictor.tex
Updates from ShareLaTeX

%\begin{raggedleft}
%{\em ``The  common misunderstanding about science 
%%is that scientists seek and find truth. They don't- 
%they make and test models.''}\\ -- Neil Gershenfeld

%{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
%%
%\end{raggedleft}

@@

>>>>

\begin{raggedleft}
{\em ``So those who are last now will be first then, \\
and those who are first will be last.''}\\ 
-- Matthew 20:16

 \end{raggedleft}

@@

\section{Motivating Example}

This section offers a small demonstration
of the impact of tuning parameters. It also demonstrates that this issue of tuning effects not jist the complex data miners discussed later in the paper but also 
applies for even very simple  learning schemes.

One way to generate a  defect predictor from
static code is to use 
linear  regression.
This is a standard statistical
method that fits a straight line to a set of points. The line
offers a set of predicted values.
If the points are somewhat
scattered, then a single regression line cannot pass through all points and the distance from these predicted values to the actual
values is a measure of the error associated with that line.
Linear regression search for a line that minimizes that
error and maximizes the correlation\footnote{
$Correlation$
measures how closely two variables co-vary.  It ranges from   from -1
(perfect negative correlation) through 0 (no correlation) to +1
 (perfect positive correlation).
Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
 the number of observations and the mean of the $n$ observations, 
respectively. Then:
$S_{PA}=\frac{\sum_i (p_i - \overline{p})(a_i -
  \overline{a})}{n-1}$ and
$S_{p}=\frac{\sum_i (p_i - \overline{p})^2}{n-1}$
and 
$S_{a}=\frac{\sum_i (a_i - \overline{a})^2}{n-1}$ and
correlation is  $c=\frac{S_{PA}}{\sqrt{S_pS_a}}$.}  denoted as $c$.

Suppose  a researcher wants to use linear regression
to test if Halstead's~\cite{halstead77} measures
of   function complexity
(number of symbols programmers has to understand) are   {\em better than}
mere lines of code for predicting
software defects.  That researcher might argue that Halstead's cognitive approach to
software bugs is better suited to code refactoring tools since it offers 
more ways to alter functions that just some coarse grained lines of code measure.

That researcher might test that belief by using studying historical
defect logs with 
linear regression. Here are two equations (learned from NASA data)
that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$.
Note that the Halstead correlations $c_2$
are worse than those from lines of code $c_1$-- which seems to suggest that
despite their potential support for refactoring, our researchers should not use Halstead.

{\scriptsize \[\begin{array}{l|l|ll}
\mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
\mathit{LOC}   &d_i= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
\mathid{Halstead & d_2= 0.231 + 0.00344N     \\    
           & +  0.0009V   - 0.185L \\
           & - 0.0343D      - 0.00541I \\
           & + 0.000019E + 0.711B \\ 
            &   - 0.00047T  & c_2=-0.36 
            \end{array}
\end{eqnarray}}

\begin{figure}[!t]
{\scriptsize
\begin{tabular}{rl}
recall   &
 \includegraphics[width=3.2in]{lsrvscostpd.pdf}\\
  false alarms:  \includegraphics[width=3.2in]{lsrvscostpf.pdf}\\
\end{tabular}}
\caption{
 probability of false alarm,
  and
  probability of recognizing defective modules  seen using \mbox{$d_i \ge T$} for
  \mbox{$0.1 \le T \le 3$} 
  Curves calculated from the KC2 dataset from the PROMISE repository goo.gl/pGDfvp
 }\label{fig:pd1}
 \end{figure}

Using these equations, a blind-spot sampling policy might be to
assess some module if $defects_i$ is more than some threshold $X_i$.
\fig{pd1} shows this for both $defects_1$ (the ``LSR'' curve) and
$defects_2$ (the ``HALSTEAD'' curve).  Not surprisingly, the detector's
$PD$ depends on the value selected for $X_i$.  At $X_i=0$ there are no
blind spots. Every part of the code is assessed so all modules with defects are found and $PD$ is very high.  But as $X_i$ increases fewer
modules are inspected, so less is found and $PD$ decreases.

 Note that either $defects_1$ or $defects_2$ can reach some desired
level of $PD$, {\em regardless of their correlations}, merely by
selecting the appropriate threshold value. For example, PD=75\% using {\em either} $defects_1\ge 0.65$ or $defects_2\ge 0.45$ (see
\fig{pd1}).
